---
title: "Prediction Assignment Writeup"
author: "Juan Carlos Rodriguez Rojo"
date: "6 de junio de 2016"
output: html_document
---

#The goal

The goal of this project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. I may use any of the other variables to predict with. I should create a report describing how I built my model, how I used cross validation, what I think the expected out of sample error is, and why I made the choices I did. I will also use my prediction model to predict 20 different test cases.

#Data loading

Data loading, data reading.
```{r}
setwd("~/WorkDoc/2016/Z_Cursos/JHOPKPracticalMachineLearning/week4/project/practicalmachinelearning/")
urlTrain <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
urlTest <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(urlTrain, destfile = "Train.csv", method = "curl")
download.file(urlTest, destfile = "Test.csv", method = "curl")
Train<-read.csv("Train.csv", header=T)
Test<-read.csv("Test.csv", header=T)
```

#Data cleaning

Thera are columns of the raw data set that contaning nothing. The first 7 columns not related to predict. We delete those columns.

```{r}
library(caret)
Train <- Train[ , colSums(is.na(Train)) == 0]
Train <- Train[, -c(1,2,3,4,5,6,7)]
Train <- Train[, -nearZeroVar(Train)]
table(Train$classe)
```

#Split data

Splitting data set to training and testing for model

```{r}
set.seed(2233)
datasplit <- createDataPartition(y=Train$classe, p = 0.7, list = FALSE)
dataTrain <- Train[datasplit,]
dataTest <- Train[-datasplit,]
```

#Model
## Tree

First model: classification tree with caret package

```{r}
library(rpart)
set.seed(3344)
modelTree <- train(classe ~ ., method = "rpart", data = dataTrain)
print(modelTree$finalModel)
predTree <- predict(modelTree, dataTest)
predTab <- with(dataTest, table(predTree, classe))
sum(diag(predTab))/sum(as.vector(predTab))
```

The accuracy is very low

## Random Forest

Second model: classification tree with random forest

```{r}
library(randomForest)
set.seed(4455)
modelRforest <- train(classe ~ ., data = dataTrain, method = "rf")
modelRforest
predRforest <- predict(modelRforest, newdata = dataTest)
confusionMatrix(predRforest, test$classe)
```

The accuracy is high now.

## Predict 20 test cases

```{r}
predRforest20<-predict(modelRforest, newdata=Test)
predRforest20
```

